### 2015-06-30 narrative/qos-app.tex
some more text on execution

%execution

>>>>

%execution
We will design an updated I/O API that will expand on the current POSIX I/O
semantics by adding new information to the I/O request. We will explore the
set of application level hints that can be easily provided to the storage
system in order for the storage system to make the most appropriate
optimization decisions. In particular, we expect the application to provide
hints on the length of time before the output data is persistent and
visible to users, and the expected lifetime of the data for data output
calls. For read calls we expect the set of hints to combine latency and
precision requirements. Additional hints will also be investigated.

We will also develop a new type of querying system that allows application
to ask the storage system about completion timing information, the response
being an estimate provided by the storage system. We will explore how these
query functions can be integrated into common applications with minimal code
disruptions, and the set of policies that applications can use to respond to
this new information. We will also explore how applications can query the
storage system to gain insights on available space in different tiers and
how applications can tailor their output data to match the available space.

Finally we will study the use of an external data annotation system that can
provide information to the storage system without requiring the application
to be recompiled.
